### 2022-04-24 paper/main.tex
Feedback from advisor and thesis defense
Record new data and update evaluation chapter
Implement Director feedback
Everything except for summaries for each section and a last look-over

\documentclass[
11pt, % The default document font size, options: 10pt, 11pt, 12pt
%oneside, % Two side (alternating margins) for binding by default, uncomment to switch to one side
english, % ngerman for German
singlespacing, % Single line spacing, alternatives: onehalfspacing or doublespacing
% draft, % Uncomment to enable draft mode (no pictures, no links, overfull hboxes indicated)
final, % Uncomment to enable final mode (hide todos)
%nolistspacing, % If the document is onehalfspacing or doublespacing, uncomment this to set spacing in lists to single
%liststotoc, % Uncomment to add the list of figures/tables/etc to the table of contents
%toctotoc, % Uncomment to add the main table of contents to the table of contents
%parskip, % Uncomment to add space between paragraphs
%nohyperref, % Uncomment to not load the hyperref package
headsepline, % Uncomment to get a line under the header
%chapterinoneline, % Uncomment to place the chapter title next to the number on one line
%consistentlayout, % Uncomment to change the layout of the declaration, abstract and acknowledgements pages to match the default layout
]{MastersDoctoralThesis} % The class file specifying the document structure

@@

\usepackage{pgfplots} % Required for the plots
\usepgfplotslibrary{statistics}
\pgfplotsset{compat=1.8}

@@

		\begin{minipage}[t]{0.4\textwidth}
			\begin{flushleft} \large
				\emph{Author:}\\
				\href{https://www.linkedin.com/in/dylanlathrum/}{\authorname} % Author name - remove the \href bracket to remove the link
			\end{flushleft}
		\end{minipage}
		\begin{minipage}[t]{0.4\textwidth}
			\begin{flushright} \large
				\emph{Supervisor:} \\
				\href{https://isearch.asu.edu/profile/3180015}{\supname} % Supervisor name - remove the \href bracket to remove the link  
			\end{flushright}
		\end{minipage}\\[3cm]

@@

	\noindent Signed:\\
	\rule[0.5em]{25em}{0.5pt} % This prints a line for the signature

	\noindent Date:\\
	\rule[0.5em]{25em}{0.5pt} % This prints a line to write the date
\end{declaration}

@@

@@

\begin{acknowledgements}
	\addchaptertocentry{\acknowledgementname} % Add the acknowledgements to the table of contents
	I would like to express my graditude to my thesis director, Dr. Robert Heinrichs, and to each of my committee members, Professor Ruben Acu\~{n}a and Dr. Shawn Jordan, for their help in the development of this thesis.
	Without their guidance, I would not have been able to step so far outside of my comfort zone and learn about so many new topics to make this thesis happen.
	I would also like to thank my friends and family who were always there to bounce ideas off of and inevitably tell me when I was trying to fit too many words into a single section.
\end{acknowledgements}

@@

\begin{abbreviations}{ll} % Include a list of abbreviations (a table of two columns)
	\addchaptertocentry{\abbrevname} % Add the Abbreviations to the table of contents
	\textbf{BOM} & \textbf{B}ill \textbf{O}f \textbf{M}aterials\\
	\textbf{CM4} & Raspberry Pi \textbf{C}ompute \textbf{M}odule \textbf{4}\\
	\textbf{CPU} & \textbf{C}entral \textbf{P}rocessing \textbf{U}nit\\
	\textbf{CRD} & \textbf{C}hrome \textbf{R}emote \textbf{D}esktop\\
	\textbf{CSV} & \textbf{C}omma \textbf{S}eparated \textbf{V}alues\\
	\textbf{FFC} & \textbf{F}lat \textbf{F}lexible \textbf{C}able\\
	\textbf{FPS} & \textbf{F}rames \textbf{P}er \textbf{S}econd\\
	\textbf{GPU} & \textbf{G}raphics \textbf{P}rocessing \textbf{U}nit\\
	\textbf{IDE} & \textbf{I}ntegrated \textbf{D}evelopment \textbf{E}nvironment\\
	\textbf{PC} & \textbf{P}ersonal \textbf{C}omputer\\
	\textbf{PCB} & \textbf{P}rinted \textbf{C}ircuit \textbf{B}oard\\
	\textbf{RDP} & \textbf{R}emote \textbf{D}esktop \textbf{P}rotocol\\
	\textbf{RTC} & \textbf{R}eal \textbf{T}ime \textbf{C}lock\\
	\textbf{SBC} & \textbf{S}ingle \textbf{B}oard \textbf{C}omputer\\
	\textbf{SMD} & \textbf{S}urface \textbf{M}ounted \textbf{D}evice\\
	\textbf{SSH} & \textbf{S}ecure \textbf{Sh}ell (Protocol)\\
	\textbf{VNC} & \textbf{V}irtual \textbf{N}etwork \textbf{C}omputing\\

@@

% \include{Chapters/Example}
\include{Chapters/Introduction}
\include{Chapters/Background}
\include{Chapters/StateOfTheArt}
\include{Chapters/Hardware}
\include{Chapters/Software}
\include{Chapters/Evaluation}
\include{Chapters/Conclusion}

@@

\include{Appendices/AppendixA}
\include{Appendices/AppendixB}
%\include{Appendices/AppendixC}

>>>>

\documentclass[
11pt, % The default document font size, options: 10pt, 11pt, 12pt
%oneside, % Two side (alternating margins) for binding by default, uncomment to switch to one side
english, % ngerman for German
singlespacing, % Single line spacing, alternatives: onehalfspacing or doublespacing
% draft, % Uncomment to enable draft mode (no pictures, no links, overfull hboxes indicated)
% final, % Uncomment to enable final mode (hide todos)
%nolistspacing, % If the document is onehalfspacing or doublespacing, uncomment this to set spacing in lists to single
%liststotoc, % Uncomment to add the list of figures/tables/etc to the table of contents
%toctotoc, % Uncomment to add the main table of contents to the table of contents
%parskip, % Uncomment to add space between paragraphs
%nohyperref, % Uncomment to not load the hyperref package
headsepline, % Uncomment to get a line under the header
%chapterinoneline, % Uncomment to place the chapter title next to the number on one line
%consistentlayout, % Uncomment to change the layout of the declaration, abstract and acknowledgements pages to match the default layout
]{MastersDoctoralThesis} % The class file specifying the document structure

@@

\usepackage{pgfplots} % Required for the plots
\usepgfplotslibrary{statistics}
\pgfplotsset{compat=1.8}
% Fix mod function bug
% borrowed from <https://tex.stackexchange.com/a/145967/95441>
\pgfmathdeclarefunction{fpumod}{2}{%
		\pgfmathfloatdivide{#1}{#2}%
		\pgfmathfloatint{\pgfmathresult}%
		\pgfmathfloatmultiply{\pgfmathresult}{#2}%
		\pgfmathfloatsubtract{#1}{\pgfmathresult}%
		% replaced `0' by `5' to make it work for this problem
		\pgfmathfloatifapproxequalrel{\pgfmathresult}{#2}{\def\pgfmathresult{5}}{}%
}

@@

		\begin{minipage}[t]{0.4\textwidth}
			\begin{flushleft} \large
				\emph{Author:}\\
				\href{https://www.linkedin.com/in/dylanlathrum/}{\authorname} % Author name - remove the \href bracket to remove the link
			\end{flushleft}
		\end{minipage}
		\begin{minipage}[t]{0.4\textwidth}
			\begin{flushright} \large
				\emph{Director:} \\
				\href{https://isearch.asu.edu/profile/3180015}{\supname} % Supervisor name - remove the \href bracket to remove the link  
			\end{flushright}
		\end{minipage}\\[.5cm]

		\begin{minipage}[t]{0.8\textwidth}
			\begin{flushright} \large
				\emph{Second Reader:}\\
				\href{https://isearch.asu.edu/profile/1232839/}{Ruben Acu\~{n}a}
			\end{flushright}
		\end{minipage}\\[.5cm]
		\begin{minipage}[t]{0.8\textwidth}
			\begin{flushright} \large
				\emph{Third Reader:} \\
				\href{https://isearch.asu.edu/profile/1625795}{Dr. Shawn Jordan}
			\end{flushright}
		\end{minipage}\\[3cm]

@@

	\noindent Signed: Dylan Lathrum\\
	\rule[0.5em]{25em}{0.5pt} % This prints a line for the signature

	\noindent Date: 4/15/2022\\
	\rule[0.5em]{25em}{0.5pt} % This prints a line to write the date
\end{declaration}

@@

This thesis will explore the development of a custom PCB that utilizes a Raspberry Pi Computer Module 4, as well as the development of a fork of the Open Source project Moonlight to stream a host machine's screen to a remote client.
This implementation will be compared against other existing remote desktop solutions to analyze it's performance and quality.

@@

\begin{acknowledgements}
	\addchaptertocentry{\acknowledgementname} % Add the acknowledgements to the table of contents
	I would like to express my graditude to my thesis director, Dr. Robert Heinrichs, and to each of my committee members, Ruben Acu\~{n}a and Dr. Shawn Jordan, for their help in the development of this thesis.
	Without their guidance, I would not have been able to step so far outside of my comfort zone and learn about so many new topics to make this thesis happen.
	I would also like to thank my friends and family who were always there to bounce ideas off of and inevitably tell me when I was trying to fit too many words into a single section.
\end{acknowledgements}

@@

\begin{abbreviations}{ll} % Include a list of abbreviations (a table of two columns)
	\addchaptertocentry{\abbrevname} % Add the Abbreviations to the table of contents
	\negmedspace % Gets rid of weird extra space
	\textbf{BOM} & \textbf{B}ill \textbf{O}f \textbf{M}aterials\\
	\textbf{CM4} & Raspberry Pi \textbf{C}ompute \textbf{M}odule \textbf{4}\\
	\textbf{CPU} & \textbf{C}entral \textbf{P}rocessing \textbf{U}nit\\
	\textbf{CRD} & \textbf{C}hrome \textbf{R}emote \textbf{D}esktop\\
	\textbf{CSV} & \textbf{C}omma \textbf{S}eparated \textbf{V}alues\\
	\textbf{FFC} & \textbf{F}lat \textbf{F}lexible \textbf{C}able\\
	\textbf{FPS} & \textbf{F}rames \textbf{P}er \textbf{S}econd\\
	\textbf{GPU} & \textbf{G}raphics \textbf{P}rocessing \textbf{U}nit\\
	\textbf{IDE} & \textbf{I}ntegrated \textbf{D}evelopment \textbf{E}nvironment\\
	\textbf{PC} & \textbf{P}ersonal \textbf{C}omputer\\
	\textbf{PCB} & \textbf{P}rinted \textbf{C}ircuit \textbf{B}oard\\
	\textbf{RDP} & \textbf{R}emote \textbf{D}esktop \textbf{P}rotocol\\
	\textbf{RTC} & \textbf{R}eal \textbf{T}ime \textbf{C}lock\\
	\textbf{SBC} & \textbf{S}ingle \textbf{B}oard \textbf{C}omputer\\
	\textbf{SMD} & \textbf{S}urface \textbf{M}ounted \textbf{D}evice\\
	\textbf{SSH} & \textbf{S}ecure \textbf{Sh}ell (Protocol)\\
	\textbf{VNC} & \textbf{V}irtual \textbf{N}etwork \textbf{C}omputing\\

@@

\include{Chapters/Introduction}
\include{Chapters/Background}
\include{Chapters/StateOfTheArt}
\include{Chapters/Hardware}
\include{Chapters/Software}
\include{Chapters/Evaluation}
\include{Chapters/Conclusion}

@@

\include{Appendices/AppendixA}
\include{Appendices/AppendixB}
\include{Appendices/AppendixC}
